Hello Window!\\\medskip \large{Felhasználói felület fejlesztés és tesztelés \textit{GTK} környezetben}

### 2011-12-30 article_window_content.tex
Fixed width settings of included graphics.

\begin{figure}[H]
\begin{center}
\subfloat[][Főablak]{\label{fig:windowprimary}\includegraphics[height=60mm]{images/window-primary.png}}
\hspace{12pt}
\subfloat[][Dialógus]{\label{fig:windowdialogl}\includegraphics[height=60mm]{images/window-dialog.png}}
\caption{Tipikus ablakszerkezetek}
\end{center}
\end{figure}

>>>>

\begin{figure}[H]
\begin{center}
\subfloat[][Főablak]{\label{fig:windowprimary}\includegraphics[height=0.35\linewidth]{images/window-primary.png}}
\hspace{12pt}
\subfloat[][Dialógus]{\label{fig:windowdialogl}\includegraphics[height=0.35\linewidth]{images/window-dialog.png}}
\caption{Tipikus ablakszerkezetek}
\end{center}
\end{figure}
